Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-13 bbbq_article.tex
Add suggested text bu @fransbianchi, progress #249

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Evolutionary conservation of TMHs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Presentation of TMH-derived epitopes \emph{in vivo}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\frans{Start}

3.4 Experimental validation of presentation and T-cell
activation of TMH-derived peptides

To obtain experimental confirmation t hat peptides stemming from TMHs are
presented in MHC-I and MHC-II, we mined the IEDB database for confirmed human
MHC-ligands from the same MHC-I and MHC-II alleles as in fig1. Figure 2A? shows the
percentages of epitopes derived from TMHs found for each of the most common MHC-
I alleles incomparison to the predictions, although ...... A single allele comparison for
MHC-II is not yet feasible as IEDB has limited reports on human MHC-II ligands for the
representative alleles.
The overall percentage of TMH derived epitopes found for
representative MHC-I and MHC-II alleles was ... and ... , respectively see Fig 2b. The
percentage of TMH derived epitopes is lower than expected from both the predictions
(Fig1) and statistical chance, however these results are affected by (I) the probed proteins/
peptides (II) the bias in mass spectrometry towards hydrophillic peptides (refs) and (III)
availablilty of data for the different alleles.
In fact these findings robustly confirm that
epitopes derived from human TMHs are presented in both MHC-I and MHC-II. See t he
supplementary Table S? for the exact values. We next mined the IEDB database for in
which T-cell responses were confirmed against specific human epitopes from the specified
alleles, from the total reports ...\% and ...\% concerned TMH derived epitopes in MHC class I
and II, respectively Fig S?. The data in Fig S? thus confirms that not only TMH derived
epitopes are presented on MHC, but also result in Immune responses.
\frans{End}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Evolutionary conservation of TMHs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Presentation of TMH-derived epitopes \emph{in vivo} in T cells}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
